Modern Statistical Methods --- Example Sheet 2

### 2020-11-10 inverse_problems/C3.tex
I'm still alive

\begin{theorem}
	Let the assumptions of \cref{thm:minimiser_existence} be satisfied and suppose that $\inf\limits_{v \in \XX} \norm{Av - f} = 0$. 
	Let $\alpha = \alpha(\delta)$ satisfy \[
	\lim_{\delta\to0} \alpha(\delta) = 0  = \limsup_{\delta \to 0} \frac{\delta^2}{\alpha(\delta)}. 
	\]
	Then any sequence $(\delta_n) \to 0$ has a subsequence $(\delta_n) \to 0$ such that $u_{\delta_n} \ceq u_{\alpha(\delta_n)} \to u_\JJ \D$ and $\JJ(u_\delta) \to \JJ(u_\JJ\D)$, where $u_\JJ\D$ is a $\JJ$-minimising solution. 
\end{theorem}

@@

>>>>

\begin{theorem} \label{thm:minimiser_convergence}
	Let the assumptions of \cref{thm:minimiser_existence} be satisfied and suppose that $\inf\limits_{v \in \XX} \norm{Av - f} = 0$. 
	Let $\alpha = \alpha(\delta)$ satisfy \[
	\lim_{\delta\to0} \alpha(\delta) = 0  = \limsup_{\delta \to 0} \frac{\delta^2}{\alpha(\delta)}. 
	\]
	Then any sequence $(\delta_n) \to 0$ has a subsequence $(\delta_n) \to 0$ such that $u_{\delta_n} \ceq u_{\alpha(\delta_n)} \to u_\JJ \D$ and $\JJ(u_\delta) \to \JJ(u_\JJ\D)$, where $u_\JJ\D$ is a $\JJ$-minimising solution. 
\end{theorem}

@@

\TODO what is the point/use of proposition 4.3.12 and corollary 4.3.13? 
%\begin{proposition}
%	Let $\Omega \subseteq \RR^n$ be a bounded Lipschitz domain, then there exists $C > 0$ such that for all $u \in \BV(\Omega)$, we have
%	\[
%	\norm{u - u_\Omega}_{L^1} \leq C \TV(u),
%	\]
%	where $u_\Omega$ is the mean value of $u$ over $\Omega$. 
%\end{proposition}

\begin{theorem}
	Let $\XX = L^1(\Omega)$, where $\Omega \subseteq \RR^n$ is bounded Lipschitz, and $\YY$ a Banach space. Let $A \in \BB(L^1, \YY)$ such that $A(1) \neq 0$. Then $u_\delta$ converges strongly in $L^1$ (along a subsequence) to a TV-minimising solution as $\delta \to 0$ if $\alpha(\delta)$ is chosen as required by \cref{thm:minimiser_convergence}. 
\end{theorem}

\begin{proof}
	We need to check that the conditions of  \cref{thm:minimiser_convergence} are satisfied. We have assumed that $\Ran(A)$ is dense, so $\inf_{v\in \XX} \norm{Av - f} = 0$. Since $\BV(\Omega)$ is compactly embedded in $L^1(\Omega)$, we know that sequences with a finite TV-value have (strongly) convergent subsequences. We have checked that $\TV$ is convex and LSC, that $\dim(\Nul(\TV)) < \infty$, and by assumption we have $\Nul(A) \cap \Nul(\TV) = \qty{0}$. Finally, $\TV$ is absolutely one-homogeneous, so all assumptions are valid. 
\end{proof}

### 2020-11-10 inverse_problems/inverse_ES2.tex
I'm still alive

% Frequently used letters in the blackboard alphabet
\newcommand{\CC}{\Bb C}
\newcommand{\NN}{\Bb N}
\newcommand{\PP}{\Bb P}
\newcommand{\QQ}{\Bb Q}
\newcommand{\RR}{\Bb R}
\newcommand{\EE}{\Bb E}
\newcommand\ZZ{\Bb Z}
\newcommand\FF{\Cal F}

@@

% Functions that appear frequently
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\Int}{Int}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand\XX{\Cal X}
\newcommand\YY{\Cal Y}
\newcommand\UU{\Cal U}
\newcommand\VV{\Cal V}
\newcommand\LL{\Cal L}
\newcommand\KK{\Cal K}
\newcommand\BB{\Cal B}
% \newcommand\LLL{\Bb L}
\DeclareMathOperator\Dom{\Cal D}
\DeclareMathOperator\Nul{\Cal N}
\DeclareMathOperator\Ran{\Cal R}
\DeclareMathOperator\diag{diag}

\title{Inverse Problems --- Example Sheet 1} % subject
\author{Lucas Riedstra}
\date{2 November 2020} % date

@@

\begin{mdframed}
		Note: when writing a norm of a vector $v \in V$, I will simply write $\norm{v}$ and not $\norm{v}_V$, unless it is unclear in which space $v$ lives. The same holds for inner products. 	
\end{mdframed}
\begin{question}
	For $\Omega = [0, 1]^2$ and $\XX \in L^2(\Omega)$, we consider the integral operator $A \colon \XX \to \XX$ with
	\[
	(Au)(y) \ceq \int_\Omega k(x, y) u(x) \dd{x},
	\]
	for $k \in L^2(\Omega \times \Omega)$.  Show that
	\begin{enumerate}[(a)]
		\item $A$ is linear with respect to $u$,
		\item $A$ is a bounded linear operator, i.e.\ $\norm{Au}_\XX \leq \norm{A}_{\LL(\XX, \XX)} \norm{u}_\XX$. Give also an estimate for $\norm{A}_{\LL(\XX, \XX)}$,
		\item the adjoint $A^*$ is given via
		\[
		(A^* v)(y) = \int_\Omega k(y, x) v(x) \dd{x}.
		\]
		\item $A$ is a compact operator, i.e.\ $A \in \KK(\XX, \XX)$.

		\emph{Hint:} you may use the fact that if an operator $A$ can be written as a limit (in the operator norm) of finite-rank operators then $A$ is compact. An operator $B$ is called finite-rank if $\dim(B) < \infty$. 
	\end{enumerate}
\end{question}

\begin{solution}

	\begin{enumerate}[(a)]
		\item Let $\alpha, \beta \in \RR$, $u, v \in L^2(\Omega)$ and $y \in \Omega$. Then we have
		\begin{align*}
			(A(\alpha u + \beta v))(y) &= \int_\Omega k(x, y) (\alpha u + \beta v)(x) \dd{x} \\
			&= \int_\Omega k(x, y) \qty(\alpha u(x) + \beta v(x)) \dd{x}\\
			&= \alpha \int_\Omega k(x, y) u(x) \dd{x} + \beta \int_\Omega k(x, y) v(x) \dd{x} \\
			&= (\alpha A u)(y) + (\beta Av)(y) = (\alpha Au + \beta Av)(y). 
		\end{align*}
	Since equality holds for all $y \in \Omega$ we find $A(\alpha u + \beta v) = \alpha A u + \beta A v$, which proves that $A$ is linear. 
	\item Let $u \in L^2(\Omega)$, then we have
	\begin{align*}
	\norm{Au}^2 &= \int_\Omega ((Au)(y))^2 \dd{y} = \int_\Omega \qty( \int_\Omega k(x, y) u(x) \dd{x})^2 \dd{y} = \int_\Omega \ang{k(\cdot, y), u(\cdot)}^2 \dd{y}. 
	\end{align*}
Now we apply Cauchy-Schwarz and find
\begin{align*}
	\int_\Omega \ang{k(\cdot, y), u(\cdot)}^2 \dd{y} &\leq \int_\Omega \norm{k(\cdot, y)}^2 \norm{u}^2 \dd{y} \overset\star= \norm{u}^2 \iint_{\Omega^2} k^2(x, y) \dd{x}\dd{y} = \norm{u}^2 \norm{k}^2, 
\end{align*}
where $\star$ follows from Fubini's theorem since the integrand is nonnegative. 
Taking square roots on both sides we find that $\norm{Au}\leq \norm{k}\norm{u}$, so $A$ is bounded with $\norm{A} \leq \norm{k}$.

\item We know that the adjoint is the unique operator that satisfies $\ang{Au, v} = \ang{u, A^*v}$ for all $u, v \in \XX$. Let $u, v \in \XX$, then we compute
\begin{align*}
	\ang{Au, v} &= \int_\Omega (Au)(y)\cdot  v(y) \dd{y} = \int_\Omega \qty(\int_\Omega k(x, y) u(x) \dd{x}) v(y) \dd{y} \\
	&= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{x} \dd{y} \overset\star= \int_\Omega\int_\Omega k(x, y) u(x) v(y) \dd{y} \dd{x} \\
	&= \int_\Omega u(x) \qty(\int_\Omega k(x, y) v(y) \dd{y}) \dd{x} = \ang{u, A^*v}
\end{align*}
where $(A^* v)(x) = \int_\Omega k(x, y) v(y) \dd{y}$ as required. Here $\star$ follows from Fubini's theorem.

\item It is known that for any compact set $X \subseteq \RR^n$, polynomials lie dense in $L^2(X)$. Therefore, there exists a sequence of polynomials $p_n$ such that $p_n \to k$ in $L^2([0, 1]^4)$. It is easily seen that for any polynomial $p$, the operator
\[
(A_p u)(y) \ceq \int_\Omega p(x, y) u(x) \dd{x} 
\] 
has finite rank: let $p(z) = \sum_{\abs{\alpha} \leq n} c_\alpha z^\alpha$ (where $z \in [0, 1]^4$ and $\alpha$ is a multi-index), then we find
\[
(A_p u)(y) = \sum_{\abs{\alpha} \leq n} c_\alpha \int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} y_1^{\alpha_3} y_2^{\alpha_4} u(x) \dd{x} = \sum_{\abs{\alpha} \leq n} c_\alpha \qty(\int_\Omega x_1^{\alpha_1} x_2^{\alpha_2} u(x) \dd{x}) y_1^{\alpha_3} y_2^{\alpha_4},
\]
so $A_p u$ lies in the $\Span\qty{y_1^{\alpha_1} y_2^{\alpha_2} \mid \alpha_1 + \alpha_2 \leq n}$, and therefore has finite rank. 
By (b), we find that $\norm{A - A_n} \leq \norm{k - p_n} \to 0$, which shows that $A_n \to A$ in operator norm. We conclude that $A$ is compact. 
%\[
%(A_n u)(y) \ceq \int_\Omega p_n()
%\]
	\end{enumerate}
\end{solution}

\begin{question}
	We consider the problem of differentiation, formulated as the inverse problem of finding $u$ from $Au = f$ with the integral operator $A \colon L^2([0, 1]) \to L^2([0, 1])$ defined as
	\[
	(Au)(y) \ceq \int_0^y u(x) \dd{x}.
	\]

	\begin{enumerate}[(a)]
		\item Let $f$ be given by
		\[
		f(x) \ceq \begin{cases} 0 & x < \frac12, \\ 1 &x > \frac12. \end{cases}
		\]
		Show that $f \in \clos{\Ran(A)}$. 
		\item Let $f$ be given as in a). Show that $f \in \clos{\Ran(A)} \setminus \Ran(A)$. \emph{Hint: Consider the Picard criterion}.

		\item Prove or falsify: ``The Moore-Penrose inverse of $A$ is continuous.''
	\end{enumerate}
\end{question}

\begin{solution}
	\begin{enumerate}[(a)]
		\item We want to show that we can approximate $f$ by a sequence $(Au_n)$ for some $(u_n) \subseteq L^2[0,1]$. To this end, define for $n \geq 2$
		\[
		u_n(x) =
		\begin{cases}
			0 &\abs{x - \frac12} > \frac1n, \\
			\frac n2 &\abs{x - \frac12} \leq \frac1n. 
		\end{cases}
		\]
		Clearly $u \in L^2[0, 1]$, and we have
		\[
		f_n(y) \ceq (Au_n)(y) = \int_0^y u_n(x) \dd{x} = \begin{cases}
			0 &\text{if $y < \frac12 - \frac1n$,}\\
			\frac n2(y - \frac12 + \frac1n) &\text{if $\frac12 - \frac1n \leq y \leq \frac12 + \frac1n$} \\
			1 &\text{if $y > \frac12 + \frac1n$}. 
		\end{cases}
		\]

		Therefore we find
		\begin{align*}
			\norm{f_n - f}^2 &= \int_0^1 (f_n - f)^2(x) \dd{x} \\
			&= 2 \int_{\frac12 - \frac1n}^{\frac12} \frac{n^2}{4} (x - \frac12 - \frac1n)^2 \dd{x} \\
			&= \frac{n^2}{2} \int_0^{1/n}  x^2 \dd{x} = \frac{1}{6n} \to 0, 
		\end{align*}
	so $f_n \to f$ in $L^2[0, 1]$. Since $f_n \in \Ran(A)$ this shows $f \in \clos{\Ran(A)}$.

	\item 	In example 2.2.12, it is shown that for this operator, the Picard criterion is
	\begin{equation} \label{eq:picard}
	2\sum_{j=1}^\infty  \sigma_j^{-2} \qty(\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s})^2 < \infty,
	\end{equation}
	where $\sigma_j = \frac2{(2j - 1)\pi}$.

	We compute
	\[
	\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s} = \int_{1/2}^1 \sin(\sigma_j^{-1} s) \dd{s} = \sigma_j \qty[ \cos(\frac12 \sigma_j^{-1}) - \cos(\sigma_j^{-1})]. 
	\]
	We have
	\[
	\cos(\sigma_j^{-1}) = \cos(\frac{(2j - 1)\pi}{2}) = 0 \quad\text{and}\quad \cos(\frac12\sigma_j^{-1}) = \cos(\frac{(2j-1)\pi}{4}) = \pm\frac1{\sqrt2 }. 
	\]

	Plugging this into \cref{eq:picard} gives that
	\[
	2\sum_{j=1}^\infty  \sigma_j^{-2} \qty(\int_0^1 f(s) \sin(\sigma_j^{-1} s) \dd{s})^2 = 2 \sum_{j=1}^\infty \sigma_j^{-2} (\sigma_j^2/2) = \sum_{j=1}^\infty 1 = \infty,
	\]
	so $f$ does not satisfy the Picard criterion and therefore $f \in \clos{\Ran(A)} \setminus \Ran(A)$. 
%	Note that $A$ is compact, since we can write $(Au)(y) = \int_{[0, 1]} k(x, y) u(x) \dd{x}$ with $k(x, y) = \ind_{x \leq y}$. 
%	
%	To apply the Picard criterion we must find the singular values and right singular vectors of $A$, which are equal to the square roots of the eigenvalues of $AA^*$ and the eigenvectors of $AA^*$. 
%	
%
%	\begin{align*}
%		\ang{Au, v} &= \int_0^1 (Au)(y)\cdot v(y) \dd{y} \\
%		&= \int_0^1 \int_0^y u(x) \dd{x} v(y) \dd{y} \\
%		&= \int_0^1 \int_0^y u(x) v(y) \dd{x} \dd{y} \\
%		&= \int_0^1 \int_x^1 u(x) v(y) \dd{y} \dd{x} \\ 
%		&= \int_0^1 u(x) \int_x^1 v(y) \dd{y} \dd{x} \\
%		&= \ang{u, A^* v}
%	\end{align*}
%where $v(x) = \int_x^1 v(y) \dd{y}$.  Therefore, we find
%\begin{align*}
%	(AA^* u)(x) = \int_0^x \int_y^1 u(z) \dd{z} \dd{y}.
%\end{align*}
%Now we solve the eigenequation. Firstly, note that $\Nul(A) = \qty{0}$, so let $\lambda^2 > 0$. Then we have
%\begin{align}
%	\int_0^x \int_y^1 u(z) \dd{z} \dd{y} &= \lambda^2 u(x) \\
%	\int_x^1 u(z) \dd{z} &= \lambda^2 u'(x) \\
%	- u(x) &= \lambda^2 u''(x). 
%\end{align}
%Furthermore, from (1) we infer $u(0) = 0$ while from (2) we infer $u'(1) = 0$. 
%The general solution to (3) is given by $u(x) = a \cos(\lambda^{-1} x) + b \sin(\lambda^{-1} x)$. 
%Plugging $u(0) = 0$ gives $a = 0$, and $u'(1) = 0$ gives
%\[
%b\lambda^{-1} \cos(\lambda^{-1}) = 0 \implies b = 0 \text{ or } \lambda^{-1} = \pi\qty(n - \frac12) \text{ for some $n \in \ZZ_{>0}$}.
%\]
%
%Our singular values are therefore $\frac{1}{(n - \frac12)\pi}$ ($n \in \ZZ_{>0}$) with right singular vectors $y_n(x) = \sqrt 2\sin((n - \frac12) \pi x)$. 
%We now compute
%\[
%\ang{f, y_n} = \sqrt 2\int_{1/2}^1 \sin(\qty(n - \frac12) \pi x) \dd{x} = ...
%\]

\item The Moore-Penrose inverse of $A$ is discontinuous. This can be seen by theorem 2.1.11: we have in (b) an element $f \in \clos{\Ran(A)} \setminus \Ran(A)$, so   $\Ran(A)$ is not closed, so $A\D$ is discontinuous.

\end{enumerate}
\end{solution}

\end{document}

>>>>

% Frequently used letters in the blackboard alphabet
\newcommand{\CC}{\Bb C}
\newcommand{\NN}{\Bb N}
\newcommand{\PP}{\Bb P}
\newcommand{\QQ}{\Bb Q}
\newcommand{\RR}{\Bb R}
\newcommand{\EE}{\Bb E}
\newcommand\XX{\Cal X}
\newcommand\YY{\Cal Y}
\newcommand\UU{\Cal U}
\newcommand\VV{\Cal V}
\newcommand\LL{\Cal L}
\newcommand\KK{\Cal K}
\newcommand\BB{\Cal B}
\newcommand\JJ{\Cal J}
\newcommand\LLL{\Bb L}
\newcommand\DD{\Cal D}

@@

% Functions that appear frequently
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\Int}{Int}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator\Dom{\Cal D}
\DeclareMathOperator\Nul{\Cal N}
\DeclareMathOperator\Ran{\Cal R}
\DeclareMathOperator\TV{TV}
\DeclareMathOperator\BV{BV}

\newcommand\cw\rightharpoonup
\newcommand\cws{\overset{*}{\rightharpoonup}}
\newcommand\rext{\overline\RR}
\newcommand\pt\partial
\DeclareMathOperator\dom{dom}

\title{Inverse Problems --- Example Sheet 2} % subject
\author{Lucas Riedstra}
\date{18 November 2020} % date

@@

\begin{question}
	Let $\UU$ be a Banach space and $J \colon \UU\to \rext$ a functional. We define the \emph{subdifferential} of $J$ at any $v \in \UU$ as
	\begin{equation} \nonumber %\label{def:subdifferentiable}
	\pt\JJ(v) \ceq \qty{p \in \UU^* \mid J(u) \geq J(v) + \ang{p, u - v} \text{ for all $u \in \UU$}}. 
	\end{equation}
	Characterise the subdifferential for the
	\begin{enumerate}[(a)]
		\item absolute value function: $\UU= \RR$, $J(v) = \abs{v}$,
		\item $\ell^1$-norm: $\UU = \ell^2$,
		\[
		J(u) = \norm{u}_{\ell^1} \ceq \begin{cases}
			\sum_{j=1}^\infty \abs{u_j} &\text{if $u \in \ell^1$}; \\ \infty &\text{else.}
		\end{cases}
		\]
		\item characteristic function of the unit ball in $\RR$: $\UU = \RR$, $J(u) = \chi_C(u)$, $C \ceq \qty{ u\in \RR : \abs{u} \leq 1}$. 
		\item Total Variation $\TV \colon L^1(\Omega) \to \rext$, where $\Omega \subset \RR^n$ is bounded Lipschitz
		\[
		\TV(u) = \sup_{\phi \in \DD} \ang{u, \div\phi}, \quad \DD = \qty{\phi \in \Cal C_0^\infty(\Omega; \RR^n) : \norm{\phi(x)}_2 \leq 1 \ \forall x \in \Omega}. 
		\]
	\end{enumerate}
\end{question}

\begin{solution}
	Note: the spaces $\UU$ in parts (a) to (c) are Hilbert spaces, which means we can identify $\UU^*$ with $\UU$ (since any functional in $\UU^*$ is of the form $\ang{u, \cdot}$ for some $u \in \UU$). 
\begin{enumerate}[(a)]
\item Let $v \in \RR$. We know that $\abs{\cdot}$ is differentiable at $v \neq 0$, so 
\[
v > 0 \implies \pt J(v) = \qty{1} \quad\text{and}\quad v < 0 \implies \pt J(v) = \qty{-1}. 
\]
For $v = 0$ we have
\begin{align*}
	p \in \pt J(v) &\iff \abs{u} \geq p \cdot u  \text{ for all $u \in \RR$} \\
	&\iff p \in [-1, 1],
\end{align*}
so $\pt J(0) = [-1, 1]$.

\item Let $v \in \ell^2$. Firstly, if $v \notin \ell^1 = \dom(J)$, then we have $\pt J(v) = \emptyset$. Assume now that $v \in \ell_1 \cap \ell_2$. Then we have, for $p \in \ell^2$, that
\begin{align}
	p \in \pt J(v) &\iff \norm{u}_{\ell^1} \geq \norm{v}_{\ell^1} + \ang{p, u - v} &\text{for all $u \in \ell^2$}  \nonumber \\
	&\iff \norm{u}_{\ell^1} - \norm{v}_{\ell^1} - \ang{p, u- v} \geq 0 &\text{for all $u \in \ell^2$} \nonumber \\
	&\iff \sum_{j=1}^\infty \abs{u_i} - \abs{v_i} - p_i(u_i - v_i) \geq 0 &\text{for all $u \in \ell^2$} \label{subdiff1} \\
	&\overset\star\iff \abs{x} - \abs{v_i} - p_i(x - v_i) \geq 0 &\text{for all $i \in \NN$ and $x \in \RR$}. \label{subdiff2}  
\end{align}
We first prove the bi-implication $\star$. If \eqref{subdiff2} holds, it is clear that \eqref{subdiff1} holds. If \eqref{subdiff2} does not hold, then we can find $x, i$ such that $\abs{x} - \abs{v_i} - p_i(x - v_i) < 0$. By now letting $u = x e_i$ in \eqref{subdiff1} we find  that \eqref{subdiff1} does not hold.

However, if we define $H(x) \ceq \abs{x}$,  we see that \cref{subdiff2} is equivalent to $p_i \in \pt H(v_i)$ for all $i$. Therefore, by (a) we have
\[
\pt J(v) = \qty{p \in \ell^2 \mid p_i = \sign(v_i) \text{ if $v_i \neq 0$ and } p_i \in [-1, 1] \text{ for all $i$}}. 
\]

\item Clearly, if $\abs{v} < 1$, then $\chi_C$ is differentiable with derivative 0 so $\pt J(v) = \qty{0}$. If $\abs{v} > 1$, then $v \notin \dom(J)$, and therefore $\pt J(v) = \emptyset$.

Consider the point $v = 1$, then we have
\[
p \in \pt J(\chi_C) \iff \chi_C(u) \geq p \cdot (u - 1) \ \forall u.
\]
For $u > 1$, this equation is satisfied regardless of $p$. Therefore, the above equation is equivalent to
\[
p \cdot(u-1) \leq 0 \ \forall u \leq 1, 
\]
which is satisfied for all $p \geq 0$, so we conclude $\pt J(1) = [0, \infty)$. 
Analogously, we find $\pt J(-1) = (-\infty, 0]$. We conclude that
\[
\pt J(v) = \begin{cases}
	\emptyset &\text{if $\abs{v} > 1$}; \\
	(-\infty, 0] &\text{if $v = -1$}; \\
	\qty{0} &\text{if $v \in (-1, 1)$}; \\
	[0, \infty) &\text{if $v = 1$}. 
\end{cases}
\]

\item 
\end{enumerate}
\end{solution}
\end{document}

### 2020-11-10 modern_statistical_methods/C2.tex
I'm still alive

Now we present the ``fast'' convergence rate of the lasso (compare with \cref{thm:lasso_slow_rate}):
\begin{theorem}[Fast rate] \label{thm:lasso_fast_rate}
	Let the conditions of \cref{thm:lasso_slow_rate} be satisfied and assume furthermore that the compatibility condition holds. 
\end{theorem}

>>>>

Now we present the ``fast'' convergence rate of the lasso (compare with \cref{thm:lasso_slow_rate}):
\begin{theorem}[Fast rate] \label{thm:lasso_fast_rate}
	Let the conditions of \cref{thm:lasso_slow_rate} be satisfied and assume furthermore that the compatibility condition holds. Then with probability at least $1 - 2p^{-(A^2/8 - 1)}$ we have
	\[
	\frac1n \norm{X(\beta^0 - \hat\beta)}_2^2 + \lambda \norm{\hat\beta - \beta^0}_1 \leq \frac{16\lambda^2s}{\phi^2} = \frac{16A^2 \log(p) \sigma^2 s}{\phi^2n }. 
	\]
\end{theorem}

\begin{proof}
	As in the proof of \cref{thm:lasso_slow_rate}, we have
	\[
	\frac1{2n} \norm{X(\beta^0 - \hat\beta)}_2^2 + \lambda \norm{\hat\beta}_1 \leq \frac1n \eps\T X(\hat\beta - \beta^0) + \lambda \norm{\beta^0}_1. 
	\]
	Define the event $\Omega = \qty{2 \norm{X\T \eps}_\infty/n \leq \lambda}$, then by H\"older's inequality we get, conditional on $\Omega$,
	\[
	\frac1n \norm{X(\hat\beta - \beta^0)}_2^2 + 2\lambda \norm{\hat\beta}_1  \leq \lambda \norm{\hat\beta - \beta^0}_1 + 2\lambda \norm{\beta^0}_1. 
	\]
	By \cref{lem:probability_omega_bound}, we find that $\PP(\Omega) \geq 1 - 2p^{-(A^2/8 - 1)}$.

	Dividing by $\lambda$, we have
	\begin{align*}
		\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 + 2 \norm{\hat\beta}_1 &\leq \norm{\hat\beta - \beta^0}_1 + 2 \norm{\beta^0}_1 \\
		\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 + 2 (\norm{\hat\beta_S}_1 + \norm{\hat\beta_N}_1) &\leq \norm{\hat\beta_S - \beta^0_S}_1 + \norm{\hat\beta_N}_1 + 2 \norm{\beta^0_S}_1\\
		\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 +  \norm{\hat\beta_N}_1 &\leq \norm{\hat\beta_S - \beta^0_S}_1 - 2 \norm{\hat\beta_S}_1 + 2 \norm{\beta^0_S}_1 \\
		&\leq 3 \norm{\hat\beta_S - \beta^0_S}_1. 
	\end{align*}
	Now we note that $\norm{\hat\beta_N}_1 = \norm{\hat\beta_N + \beta^0_N}_1$, and we add $\norm{\hat\beta_S - \beta^0_S}_1$ to both sides of the inequality to get
	\begin{equation} \label{eq:error_inequality}
	\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 + \norm{\hat\beta - \beta^0}_1  \leq 4 \norm{\beta_S - \beta^0_S}_1. 
	\end{equation}
	Assume that $\norm{\hat\beta - \beta^0} \neq 0$ (otherwise the theorem is definitely true), and note that $\norm{(\hat\beta - \beta^0)_N}_1 \leq 3 \norm{\hat\beta}_1 \leq 3 \norm{(\hat \beta - \beta^0)_S}$ by our previous inequality, we find that the compatibility constant satisfies
	\[
	\phi^2 \leq \frac{\frac1n \norm{X(\hat\beta - \beta^0)}_2^2}{\frac1s \norm{\hat\beta - \beta^0}_1^2} \implies \frac1{\phi} \geq \sqrt{\frac ns} \frac{\norm{\hat\beta - \beta^0}_1}{\norm{X(\hat\beta - \beta^0)}_2},
	\]
	and plugging this into \cref{eq:error_inequality} we get
	\begin{equation} \label{eq:error_inequality_2}
	\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 + \norm{\hat\beta - \beta^0}_1  \leq 4 \norm{\beta_S - \beta^0_S}_1 \leq \frac4\phi \sqrt{\frac sn} \norm{X(\hat\beta - \beta^0)}_2,
	\end{equation}
	or equivalently
	\[
	\frac1{\lambda n} \norm{X(\hat\beta - \beta^0)}_2^2 - \frac4\phi \sqrt{\frac sn} \norm{X(\hat\beta - \beta^0)}_2 + \norm{\hat\beta - \beta^0}_1 \leq 0. 
	\]
	This is a quadratic inequality in $\norm{X(\hat\beta - \beta^0)}_2$, and solving it yields
	\[
	\frac1{\sqrt n} \norm{X(\hat\beta - \beta^0)}_2 \leq \frac{4\lambda \sqrt s}{\phi}. 
	\] 
	Plugging that into the right hand side of \cref{eq:error_inequality_2} yields the required result. 
\end{proof}
